Identification of high-yielding soybean lines with exceptional seed composition qualities

### 2022-04-26 doc/manuscript/manuscript.Rmd
Some small changes to the targets file to use the here functioninstead of absolute file paths

Soybean lines typically contain about 20\% oil and 40\% protein content on a dry weight basis[@ProteinGenomics]. The market for soybean meal requires 47.5\% protein content in the meal, which corresponds to approximately 41.5\% protein content on a dry weight basis[@ProteinGenomics]. Oil and protein content are two of the most important seed composition traits in soybean so if one is decreased, the other should be correspondingly increased to account for the loss in value. The inverse correlation between protein and oil contents is well known and is suspected to be due at least partially to the action of pleiotropic genes and competing metabolic pathways which control the expression of each trait[@SeedCompositionGenomics].

Despite the difficulty in simultaneously breeding for all three of these traits, releases of varieties with elevated protein contents and only moderately reduced yield has shown that it is not impossible. The high protein germplasm lines R05-1415 and R05-1772 were released recently and contain 46.9\% and 46.1\% protein content with while still producing yields 94\% and 91\% of that of the high yielding 5002T cultivar[@HiProtHiYield02]. Lines TN03-350 and TN04-5321 contain 43.9\% and 43.1\% protein content while having superior or comparable performance to yield checks[@HiProtHiYield04]. The Prolina cultivar has a protein content of 46.1\% with a yield only 13\% reduced from the Centennial check[@HiProtHiYield01]. The Highpro1 cultivar was released in 2016 and has a yield which is greater than or equal to 97\% of that of the highest yielding check cultivar, IA3023 with a protein content of 40.1\%[@HighPro1]. Cultivars produced through conventional breeding techniques such as these have shown that it is possible to identify lines with both high seed protein and seed yield. Efforts to find these lines should be continued to provide growers and breeders with additional high value cultivars, and germplasm which can be further used to improve protein and yield traits.

@@

## Population development
In 2018, oil mapping populations 201 and 202 were grown as plant rows at the Central Crops Research Station in Clayton, NC. These populations consisted of 273 and 237 recombinant inbred lines (RILs) respectively. Several agronomic traits were scored in the field for each population.

The agronomic traits recorded in the field were height, lodging, maturity date, and a composite agronomic score. Lodging was scored on a scale of 1-5 where 5 indicates that all plants in a plot are on the ground, and a score of 1 indicates that all plants are erect[@fehr1987soybeans]. The agronomic score aimed to capture other traits of value such as visual estimation of pod load and plot uniformity to provide a general score of a line’s agronomic desirability. Agronomic score was recorded on a scale of 1-5 as well, with 1 identifying the best lines of a population, and 5 the worst. Maturity was recorded at the R8 maturity date and was recorded as the number of days after September 1. Height was measured in inches from the soil to the top of the plant.

@@

## Statistical Analysis
Phenotypic traits were analysed with a linear model with the form:

@@

* First bullet
* Second bullet
* Third bullet

@@

\begin{figure}[H]
\centering
\includegraphics[width=10 cm]{`r example_plot`}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=3 cm]{logo-mdpi}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

\begin{table}[H]
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
entry 1		& data			& data\\
entry 2		& data			& data\\
\bottomrule
\end{tabular}
\end{table}

```{r test_table, results = "asis", echo = FALSE}
print(example_table)
```

@@

<!-- Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows: -->
Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

>>>>

Soybean lines typically contain about 20% oil and 40% protein content on a dry weight basis[@ProteinGenomics]. The market for soybean meal requires 47.5% protein content in the meal, which corresponds to approximately 41.5% protein content on a dry weight basis[@ProteinGenomics]. Oil and protein content are two of the most important seed composition traits in soybean so if one is decreased, the other should be correspondingly increased to account for the loss in value. The inverse correlation between protein and oil contents is well known and is suspected to be due at least partially to the action of pleiotropic genes and competing metabolic pathways which control the expression of each trait[@SeedCompositionGenomics].

Despite the difficulty in simultaneously breeding for all three of these traits, releases of varieties with elevated protein contents and only moderately reduced yield has shown that it is not impossible. The high protein germplasm lines R05-1415 and R05-1772 were released recently and contain 46.9% and 46.1% protein content with while still producing yields 94% and 91% of that of the high yielding 5002T cultivar[@HiProtHiYield02]. Lines TN03-350 and TN04-5321 contain 43.9% and 43.1% protein content while having superior or comparable performance to yield checks[@HiProtHiYield04]. The Prolina cultivar has a protein content of 46.1% with a yield only 13% reduced from the Centennial check[@HiProtHiYield01]. The Highpro1 cultivar was released in 2016 and has a yield which is greater than or equal to 97% of that of the highest yielding check cultivar, IA3023 with a protein content of 40.1%[@HighPro1]. Cultivars produced through conventional breeding techniques such as these have shown that it is possible to identify lines with both high seed protein and seed yield. Efforts to find these lines should be continued to provide growers and breeders with additional high value cultivars, and germplasm which can be further used to improve protein and yield traits.

@@

## Population development

In 2018, oil mapping populations 201 and 202 were grown as plant rows at the Central Crops Research Station in Clayton, NC. These populations consisted of 273 and 237 recombinant inbred lines (RILs) respectively. Several agronomic traits were scored in the field for each population.

The agronomic traits recorded in the field were height, lodging, maturity date, and a composite agronomic score. Lodging was scored on a scale of 1-5 where 5 indicates that all plants in a plot are on the ground, and a score of 1 indicates that all plants are erect[@fehr1987soybeans]. The agronomic score aimed to capture other traits of value such as visual estimation of pod load and plot uniformity to provide a general score of a line's agronomic desirability. Agronomic score was recorded on a scale of 1-5 as well, with 1 identifying the best lines of a population, and 5 the worst. Maturity was recorded at the R8 maturity date and was recorded as the number of days after September 1. Height was measured in inches from the soil to the top of the plant.

@@

## Statistical Analysis

Phenotypic traits were analysed with a linear model with the form:

@@

-   First bullet
-   Second bullet
-   Third bullet

@@

```{=tex}
\begin{figure}[H]
\centering
\includegraphics[width=10 cm]{`r example_plot`}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}
```
```{=tex}
\begin{figure}[H]
\centering
\includegraphics[width=3 cm]{logo-mdpi}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}
```
```{=tex}
\begin{table}[H]
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Title 1}    & \textbf{Title 2}  & \textbf{Title 3}\\
\midrule
entry 1     & data          & data\\
entry 2     & data          & data\\
\bottomrule
\end{tabular}
\end{table}
```
```{r test_table, results = "asis", echo = FALSE}
print(example_table)
```

@@

<!-- Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows: -->

Example of a theorem:

```{=tex}
\begin{Theorem}
Example text of a theorem.
\end{Theorem}
```
The text continues here. Proofs must be formatted as follows:

Example of a proof:

```{=tex}
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
\end{proof}
```
The text continues here.
